The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
model comparison times

This method of automated vetting is clearly limited by the specific models
selected in this step.
We find that these are sufficient for the targets discussed below but other
target lists might require additional models to be included for robust
selection.

@@

\dfmfig{model-comp}

>>>>

\dfmfig{model-comp} shows representative events that fall into different
classes and the corresponding maximum-likelihood model.

The reliability of this method of automated vetting is limited by the specific
models selected in this step.
We find that these are sufficient for the targets discussed below but other
target lists might require additional models to be included for robust
selection.

@@
